Asteroseismology: AI-Driven Seismic Event Detection for Extra-Terrestrial Missions\\

### 2025-05-25 paper.tex
checkpoint, final

        More recently, with the digitization and improved accessibility of Apollo data, new analytical techniques have
        been applied. Traditional methods continue to be refined, for example, for re-evaluating Apollo 17 LSPE data
        (Heffels et al., 2017). Machine learning has also begun to make inroads. Knapmeyer-Endrun \& Hammer (2015)
        utilized Hidden Markov Models for event detection in Apollo 16 data. Significantly, Civilini et al. (2021)
        demonstrated the successful application of Convolutional Neural Networks (CNNs), trained on spectrograms of
        Earth-based seismic events via transfer learning, to detect and catalog moonquakes from both PSE and LSPE data.
        This approach highlighted the potential of ML to identify events even with limited or non-local training data,
        by learning characteristic spectral features. Majstorović et al. (2024, preprint/submitted) further explored ML
        by using random forests to classify DMQ source regions based on lunar orbital parameters related to their
        occurrence times, showcasing an approach independent of waveform data for initial source region estimation.

@@

>>>>

        More recently, with the digitization and improved accessibility of Apollo data, new analytical techniques have
        been applied. Traditional methods continue to be refined, for example, for re-evaluating Apollo 17 LSPE data
        \cite{Heffels2017}. Machine learning has also begun to make inroads.\cite{Knapmeyer2015} utilized Hidden Markov
        Models for event detection in Apollo 16 data. Significantly, \cite{Civilini2021} demonstrated the successful
        application of Convolutional Neural Networks (CNNs), trained on spectrograms of Earth-based seismic events via
        transfer learning, to detect and catalog moonquakes from both PSE and LSPE data. This approach highlighted the
        potential of ML to identify events even with limited or non-local training data, by learning characteristic
        spectral features.

@@

    \bibitem{Heffels2017} A. Heffels, R. F. Garcia, and M. Drilleau, ``Re-evaluation of Apollo 17 lunar seismic profiling experiment data,'' \emph{Planetary and Space Science}, vol. 135, pp. 43--54, 2017.
    \bibitem{Knapmeyer2015} B. Knapmeyer-Endrun and C. Hammer, ``Identification of new events in Apollo 16 lunar seismic data by Hidden Markov Model-based event detection and classification,'' \emph{J. Geophys. Res. Planets}, vol. 120, no. 10, pp. 1620--1645, Oct. 2015.
